---
title: "STAT 140 - Lab 8"
subtitle: "Sampling distributions and the Central Limit Theorem"
author: "YOUR NAME HERE"
date: "3/30/2020"
output: html_document
---

```{r setup, include=FALSE}
## Optional lines to run if you haven't installed packages on your computer:
## Uncomment to run, then comment out again
# install.packages("ggplot2")
# install.packages("readr")

## Load packages
library(ggplot2)
library(readr)
library(dplyr)
```


# Sampling distribution - Roosevelt Dimes

For this lab, we will be working with data about United States Roosevelt dimes (the dimes you typically see if you get change). I have compiled a data set with their mintages (number of dimes produced) by year, from 1948, when they were first produced, to 2018. We will be using these data to explore sampling distributions.

```{r}
## Read in coin data
roosevelt_dimes <- read_csv("https://marievozanne.github.io/roosevelt_dimes.csv")

## Add column for probabilities
roosevelt_dimes$Probability <- roosevelt_dimes$Mintage/sum(roosevelt_dimes$Mintage)

## Add indicator (0/1) column for coins after 2000 - 0 if before, 1 otherwise
roosevelt_dimes$Ind_After2000 <- rep(0, nrow(roosevelt_dimes))
roosevelt_dimes[roosevelt_dimes$Year > 1999,]$Ind_After2000 <- 1
```

## Sample mean

#### Make a scatterplot of Mintage versus Year. Add a line connecting the points using `geom_line()`.

```{r}

```

#### Use the following code to make a new data set of the years.

```{r}
parent_Year <- data.frame(Year=sample(roosevelt_dimes$Year, prob=roosevelt_dimes$Probability, replace=TRUE, size=10000))
```

#### Using `parent_Year`, make a histogram of the dime mintage years. Does the distribution of mintage years appear to be normal?

```{r}

```

#### Use the following code to generate 1000 samples of size 5 and find the average mintage year for each sample. We will use this to plot a sampling distribution for the average mintage year for samples of size 5 (n=5).

```{r}
avg_year <- rep(NA, 1000)
for (i in 1:1000){
  avg_year[i] <- mean(sample(roosevelt_dimes$Year, prob=roosevelt_dimes$Probability, replace=TRUE, size=5))
}

sampling_AvgYear_n5 <- data.frame(avg_year=avg_year)
```

#### Using `sampling_AvgYear_n5`, make a histogram of the average dime mintage years. Does the sampling distribution appear to be normal?

```{r}

```

#### Based on what you know about the Central Limit Theoreom, can you say that the sampling distribution (for n=5) is approximately normal?






#### Use the following code to generate 1000 samples of size 30 and find the average mintage year for each sample. We will use this to plot a sampling distribution for the average mintage year for samples of size 30 (n=30).

```{r}
avg_year <- rep(NA, 1000)
for (i in 1:1000){
  avg_year[i] <- mean(sample(roosevelt_dimes$Year, prob=roosevelt_dimes$Probability, replace=TRUE, size=30))
}

sampling_AvgYear_n30 <- data.frame(avg_year=avg_year)
```

#### Using `sampling_AvgYear_n30`, make a histogram of the average dime mintage years. Does the sampling distribution appear to be normal?

```{r}

```

#### Find the mean and standard deviation of `sampling_AvgYear_n30`. Save them as `mean_n30` and `sd_n30`, respectively.

```{r}

```

#### Based on what you know about the Central Limit Theoreom, can you say that the sampling distribution (for n=30) is approximately normal? What are the mean and the standard error for this distribution?






#### Use the following code to generate 1000 samples of size 50 and find the average mintage year for each sample. We will use this to plot a sampling distribution for the average mintage year for samples of size 50 (n=50).

```{r}
avg_year <- rep(NA, 1000)
for (i in 1:1000){
  avg_year[i] <- mean(sample(roosevelt_dimes$Year, prob=roosevelt_dimes$Probability, replace=TRUE, size=50))
}

sampling_AvgYear_n50 <- data.frame(avg_year=avg_year)

```

#### Find the mean and standard deviation of `sampling_AvgYear_n50`. Save them as `mean_n50` and `sd_n50`, respectively. How do they compare to `mean_n30` and `sd_n30`?

```{r}

```


## Sample proportion

In the exercises above, we looked at sampling distributions for the sample mean. We can also look at sampling distributions for the sample proportion. For this, we will use the `Ind_After2000` variable.

#### Use the following code to generate 1000 samples of size 5 and find the proportion of successes (coin minted in 2000 or later). We will use this to plot a sampling distribution for the sample proportion for samples of size 5 (n=5).

```{r}
n <- 5

samp_prop <- rep(NA, 1000)
for (i in 1:1000){
  samp_prop[i] <- mean(sample(roosevelt_dimes$Ind_After2000, prob=roosevelt_dimes$Probability,
                             replace=TRUE, size=n))
}

sampling_samp_prop_n5 <- data.frame(samp_prop=samp_prop)
```

#### Using `sampling_samp_prop_n5`, make a histogram of the average dime mintage years. Does the sampling distribution appear to be normal? Check your conditions, $np \geq 10$ and $n(1-p) \geq 10`$ to see if the conditions for approximate normality (and the Central Limit Theorem) are satisfied.

```{r}

```

#### Use the following code to generate 1000 samples of size 50 and find the proportion of successes (coin minted in 2000 or later). We will use this to plot a sampling distribution for the sample proportion for samples of size 50 (n=50).

```{r}
n <- 50

samp_prop <- rep(NA, 1000)
for (i in 1:1000){
  samp_prop[i] <- mean(sample(roosevelt_dimes$Ind_After2000, prob=roosevelt_dimes$Probability,
                             replace=TRUE, size=n))
}

sampling_samp_prop_n50 <- data.frame(samp_prop=samp_prop)

hist(sampling_samp_prop_n50$samp_prop)
```

#### Using `sampling_samp_prop_n50`, make a histogram of the average dime mintage years. Does the sampling distribution appear to be normal? Check your conditions, $np \geq 10$ and $n(1-p) \geq 10`$ to see if the conditions for approximate normality (and the Central Limit Theorem) are satisfied.

```{r}

```

#### Use the following code to generate 1000 samples of size 100 and find the proportion of successes (coin minted in 2000 or later). We will use this to plot a sampling distribution for the sample proportion for samples of size 100 (n=100).

```{r}
n <- 100

samp_prop <- rep(NA, 1000)
for (i in 1:1000){
  samp_prop[i] <- mean(sample(roosevelt_dimes$Ind_After2000, prob=roosevelt_dimes$Probability,
                             replace=TRUE, size=n))
}

sampling_samp_prop_n100 <- data.frame(samp_prop=samp_prop)

hist(sampling_samp_prop_n100$samp_prop)
```

#### Using `sampling_samp_prop_n100`, make a histogram of the average dime mintage years. Does the sampling distribution appear to be normal? Check your conditions, $np \geq 10$ and $n(1-p) \geq 10`$ to see if the conditions for approximate normality (and the Central Limit Theorem) are satisfied.

```{r}

```

## Independence assumption

An underlying assumption of the Central Limit Theorem is that the observations in each sample are independent. Based on what you know about the sample function in R, do you think the independence assumption is satisfied?

